---
title: "Main Analysis"
output:
  html_document:
    df_print: paged
---

Load libraries
```{r}
library(stargazer)
library(haven)
library(dplyr)
library(lfe)
library(ggplot2)
library(htmltools)
library(broom)

```




Define filepaths
```{r}
# encrypted drive path
# Brian
#encripted_drive_path <- "/Volumes/Untitled/PA DOC/"
 
# Neil mac
encripted_drive_path <- "/Users/silveus/Documents/Data/PA DOC/" 
# Neil PC 
#encripted_drive_path <- "" 

# analysis path
analysis_datapath <- paste0(encripted_drive_path,"/analysis data")
 

```
## Build analysis with fake data
```{r}

# Set seed for reproducibility
set.seed(123)

# Number of rows in the dataset
num_rows <- 10000

# Generate fake data
arrival_FAKE_reg_data_facility <- tibble(
  year = sample(2008:2024, num_rows, replace = TRUE),
  quarter = sample(1:4, num_rows, replace = TRUE),
  avelsir = runif(num_rows, 0, 1),
  aveage = rnorm(num_rows, mean = 36, sd = 7),
  arrivals_black=round(runif(num_rows,0,10)),
  arrivals_drug=round(runif(num_rows,0,15)),
  arrivals_violent=round(runif(num_rows,0,7)),
  arrivals_property=round(runif(num_rows,0,9)),
  arrivals_public=round(runif(num_rows,0,5)),
  loc = sample(paste0("LOC", 1:150), num_rows, replace = TRUE),
  ccf = sample(0:1, num_rows, replace = TRUE)
)

# Modify avelsir to fake treatment effect
arrival_FAKE_reg_data_facility <- arrival_FAKE_reg_data_facility %>%
  mutate(avelsir = ifelse((ccf==1)&(year > 2013 | (year == 2013 & quarter >= 3)),
                          rnorm(n(), mean = .25, sd = 0.001),  # New distribution for ccfs after treatment: normal with mean 0.25 and sd 0.001
                          avelsir))



```




<!-- Import analysis data -->
<!-- ```{r} -->
<!-- indiv_arrival_reg_data <- read.csv(paste0(analysis_datapath,"FILENAME")) -->
<!-- arrival_reg_data_facility read.csv(paste0(analysis_datapath,"FILENAME")) -->
<!-- ``` -->




<!-- How do arrivals to CCFs compare to arrivals to CCCs prior to 2013? The below requires a dataset for analysis that has a dummy variable for post (>= 2013) and a dummy variable for ccf(1 if ccf, 0 if ccc). The dataset should be individual arrivals. -->
<!-- ```{r} -->
<!-- balancereg1 <- felm(lsir~ccf,reg_data[reg_data$post==0]) -->
<!-- balancereg2 <- felm(black~ccf,reg_data[reg_data$post==0]) -->
<!-- balancereg3 <- felm(age~ccf,reg_data[reg_data$post==0]) -->
<!-- balancereg4 <- felm(drugoffence~ccf,reg_data[reg_data$post==0]) -->
<!-- balancereg5 <- felm(violentoffence~ccf, reg_data[reg_data$post==0]) -->
<!-- balancereg6 <- felm(arrivals <- ccf, reg_data[reg_data$post==0] %>%  -->
<!--                                                 group_by(loc,month) %>%  -->
<!--                                                 summarise(arrivals=n()), -->
<!--                                                           ccf=first(ccf), -->
<!--                                                           post=first(post)) -->


<!-- htmloutput <- stargazer(balangereg1,balangereg2,balangereg3,balangereg4,balangereg5,balancereg6, type = "html") -->

<!-- html_print(HTML(htmloutput)) -->
<!-- ``` -->

<!-- ## Baseline DID -->

<!-- ### Risk Scores -->
<!-- ```{r} -->
<!-- reg1 <- felm(avelsir ~ ccf + post + ccf*post year region avenumberarrivals2008_2010 avelsir2008_2010 avepctblack2008_2010 |loc + year + calandermonth|0|0, data=reg_data) -->
<!-- reg2 <- felm(avelsir ~ ccf + post + ccf*post |loc + year + calandermonth|0|0, data=reg_data) -->

<!-- htmloutput <- stargazer(reg1,reg2, type = "html") -->

<!-- html_print(HTML(htmloutput)) -->
<!-- ``` -->

<!-- ### Race -->
<!-- ```{r} -->
<!-- reg1 <- felm(blackarrivals ~ ccf + post + ccf*post year region avenumberarrivals2008_2010 avelsir2008_2010 avepctblack2008_2010 |loc + year + calandermonth|0|0, data=reg_data) -->
<!-- reg2 <- felm(blackarrivals ~ ccf + post + ccf*post |loc + year + calandermonth|0|0, data=reg_data) -->

<!-- htmloutput <- stargazer(reg1,reg2, type = "html") -->

<!-- html_print(HTML(htmloutput)) -->
<!-- ``` -->

<!-- ### Offence Types -->
<!-- ```{r} -->
<!-- # Violent -->
<!-- reg1 <- felm(arrivals_violent ~ ccf + post + ccf*post year region avenumberarrivals2008_2010 avelsir2008_2010 avepctblack2008_2010 |loc + year + calandermonth|0|0, data=reg_data) -->
<!-- reg2 <- felm(arrivals_violent ~ ccf + post + ccf*post |loc + year + calandermonth|0|0, data=reg_data) -->

<!-- # Drug -->
<!-- reg1 <- felm(arrivals_drug ~ ccf + post + ccf*post year region avenumberarrivals2008_2010 avelsir2008_2010 avepctblack2008_2010 |loc + year + calandermonth|0|0, data=reg_data) -->
<!-- reg2 <- felm(arrivals_drug ~ ccf + post + ccf*post |loc + year + calandermonth|0|0, data=reg_data) -->

<!-- # Property -->
<!-- reg1 <- felm(arrivals_property ~ ccf + post + ccf*post year region avenumberarrivals2008_2010 avelsir2008_2010 avepctblack2008_2010 |loc + year + calandermonth|0|0, data=reg_data) -->
<!-- reg2 <- felm(arrivals_property ~ ccf + post + ccf*post |loc + year + calandermonth|0|0, data=reg_data) -->
<!-- htmloutput <- stargazer(reg1,reg2, type = "html") -->

<!-- # Public Order -->
<!-- reg1 <- felm(arrivals_public ~ ccf + post + ccf*post year region avenumberarrivals2008_2010 avelsir2008_2010 avepctblack2008_2010 |loc + year + calandermonth|0|0, data=reg_data) -->
<!-- reg2 <- felm(arrivals_public ~ ccf + post + ccf*post |loc + year + calandermonth|0|0, data=reg_data) -->
<!-- htmloutput <- stargazer(reg1,reg2,reg3, reg4, reg5, reg6, reg7, reg8, type = "html") -->


<!-- html_print(HTML(htmloutput)) -->
<!-- ``` -->



## Baseline Event Studies

The basic event study for facility level analyses will take the following form:

$$
y_{ft}=\alpha+CCF_f\times\sum^{14}_{\substack{\tau=-14}\\ \tau\neq -1}\beta_{\tau}I(t-t^*=\tau)+\gamma_f +\lambda_t+\epsilon_{ft}
$$
Where: 

* $\alpha$: Constant
* $CCF$: Dummy variable equal to 1 if facility if CCF
* $I(t-t^*=\tau)$: $t^*$ is the time period of treatment. $I(t-t^*=\tau)$ is an indicator function that is equal to one if $t$ is $\tau$ periods from treatment
* $gamma_f$ and $lambda_t$ are facility and period fixed effects respectively


### Create a function to create an event study graph using the specification above
```{r}
make_es <- function(pre_period_num,post_period_num,outcome_variable, treatment_date, data, confidence_interval=0.95, graph_label="Enter graph label"){

trt_year <- as.numeric(substr(treatment_date, 5, 8))
trt_month <- as.numeric(substr(treatment_date,1,2))
trt_quarter <- ceiling(4*(trt_month/12))


es_data <- data %>% arrange(year, quarter) %>% group_by(year, quarter) %>% mutate(period_index=cur_group_id()) %>% ungroup()

es_data <- es_data %>% mutate(post=ifelse(year>trt_year|(year==trt_year & quarter>=trt_quarter),1,0))

#get index number for the treatment period. The result is an integer.
trt_index <- es_data %>% filter(year==trt_year, quarter==trt_quarter) %>% distinct(year,quarter,.keep_all = TRUE) %>% pull("period_index")

#recenter the periods so that the treatment period is indexed as zero
es_data <- es_data %>% mutate(period_index=period_index-trt_index)

#keep only observations within the specified event window
es_data <- es_data %>% filter(period_index<=post_period_num & period_index>=-1*(pre_period_num))

# Convert 'period_index' to factor and set reference level to "-1"
es_data$period_factor <- relevel(factor(es_data$period_index), ref = "-1")

# Ensure 'outcome_variable' exists in the data
if (!outcome_variable %in% names(es_data)) {
  stop(paste("The outcome variable", outcome_variable, "is not found in the dataset"))
}


# Fit the fixed effects model
formula <- as.formula(paste(outcome_variable, "~ ccf * period_factor | loc | 0 | 0")) # note that this syntax fits a model with ccf and period_factor fixed effects as well as the interaction
es_reg <- felm(formula, es_data)

# Extract coefficients
coefficients <- summary(es_reg)$coefficients

# Convert coefficients to data frame
coef_df <- data.frame(
  term = rownames(coefficients),
  estimate = coefficients[, "Estimate"],
  std.error = coefficients[, "Std. Error"]
)

# Keep event study coefficients
coef_df <- coef_df %>%
  filter(grepl("ccf", term) & grepl("period_factor", term))

#Manually add omitted coefficient
ref_coeff <- data.frame(
    term = "ccf:period_factor-1",
    estimate = 0,
    std.error = 0
)

coef_df <- rbind(coef_df, ref_coeff)

# Add confidence intervals
zscore=qnorm((1-confidence_interval)/2+confidence_interval)
coef_df <- coef_df %>%
  mutate(
    conf.low = estimate - zscore * std.error,
    conf.high = estimate + zscore * std.error
  )

# Specify the desired order for the period factors
desired_order <- paste0("ccf:period_factor", -pre_period_num:post_period_num)
coef_df <- coef_df %>%
  mutate(term = factor(term, levels = desired_order)) %>%
  arrange(term)


# Plot the coefficients
ggplot(coef_df, aes(x = term, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_discrete(
    breaks = desired_order[seq(1, length(desired_order), by = 2)],  # Set breaks for every other tick
    labels = as.character(seq(-pre_period_num, post_period_num, by = 2))  # Customize labels
  ) +
  labs(title = graph_label,
       x = "Event Time (quarters)",
       y = "")
}

#number of pre periods
pre_period_num=14
#number of post periods
post_period_num=14
#outcome variable
outcome_variable <- 'avelsir'
#define treatment date MMDDYYY
treatment_date <- "07012013"



```


### Average LSIR event study
```{r}
make_es(pre_period_num = 14, post_period_num = 14, outcome_variable = 'avelsir', treatment_date = '07012013', data = arrival_FAKE_reg_data_facility, confidence_interval = 0.95, graph_label = "Average LSIR of Arrivals: FAKE DATA")
```

### Average age event study

```{r}
make_es(pre_period_num = 14, post_period_num = 14, outcome_variable = 'aveage', treatment_date = '07012013', data = arrival_FAKE_reg_data_facility, confidence_interval = 0.95, graph_label = "Average Age of Arrivals: FAKE DATA")
```

### Number of black arrivals event study
```{r}
make_es(pre_period_num = 14, post_period_num = 14, outcome_variable = 'arrivals_black', treatment_date = '07012013', data = arrival_FAKE_reg_data_facility, confidence_interval = 0.95, graph_label = "# of Black arrivals: FAKE DATA")
```



### Number of drug offense arrivals event study
```{r}
make_es(pre_period_num = 14, post_period_num = 14, outcome_variable = 'arrivals_drug', treatment_date = '07012013', data = arrival_FAKE_reg_data_facility, confidence_interval = 0.95, graph_label = "# Drug offense arrivals: FAKE DATA")
```


### Number of violent offense arrivals event study
```{r}
make_es(pre_period_num = 14, post_period_num = 14, outcome_variable = 'arrivals_violent', treatment_date = '07012013', data = arrival_FAKE_reg_data_facility, confidence_interval = 0.95, graph_label = "# Violent offense arrivals: FAKE DATA")
```

### Number of property offense arrivals event study
```{r}
make_es(pre_period_num = 14, post_period_num = 14, outcome_variable = 'arrivals_property', treatment_date = '07012013', data = arrival_FAKE_reg_data_facility, confidence_interval = 0.95, graph_label = "# Property offense arrivals: FAKE DATA")
```

 ### Number of public order offense arrivals event study
```{r}
make_es(pre_period_num = 14, post_period_num = 14, outcome_variable = 'arrivals_violent', treatment_date = '07012013', data = arrival_FAKE_reg_data_facility, confidence_interval = 0.95, graph_label = "# Public order offense arrivals: FAKE DATA")
```


