---
title: "Main Analysis"
output:
  html_document:
    df_print: paged
---

Load libraries
```{r}
library(stargazer)
library(haven)
library(dplyr)
library(lfe)
library(ggplot2)
library(htmltools)

```


```{r}
mtcars %>% View()
```

```{r}
mtcars %>% group_by(mpg,cyl) %>% summarise(count=n(), .groups = 'drop') %>% View()
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.




Define filepaths
```{r}
# encrypted drive path
# Brian
#encripted_drive_path <- "/Volumes/Untitled/PA DOC/"
 
# Neil mac
encripted_drive_path <- "/Users/silveus/Documents/Data/PA DOC/" 
# Neil PC 
#encripted_drive_path <- "" 

# analysis path
analysis_datapath <- paste0(encripted_drive_path,"/analysis data")
 

```



Import analysis data
```{r}
indiv_arrival_reg_data <- read.csv(paste0(analysis_datapath,"FILENAME"))
facility_a
```




How do arrivals to CCFs compare to arrivals to CCCs prior to 2013? The below requires a dataset for analysis that has a dummy variable for post (>= 2013) and a dummy variable for ccf(1 if ccf, 0 if ccc). The dataset should be individual arrivals.
```{r}
balancereg1 <- felm(lsir~ccf,reg_data[reg_data$post==0])
balancereg2 <- felm(black~ccf,reg_data[reg_data$post==0])
balancereg3 <- felm(age~ccf,reg_data[reg_data$post==0])
balancereg4 <- felm(drugoffence~ccf,reg_data[reg_data$post==0])
balancereg5 <- felm(violentoffence~ccf, reg_data[reg_data$post==0])
balancereg6 <- felm(arrivals <- ccf, reg_data[reg_data$post==0] %>% 
                                                group_by(loc,month) %>% 
                                                summarise(arrivals=n()),
                                                          ccf=first(ccf),
                                                          post=first(post))


htmloutput <- stargazer(balangereg1,balangereg2,balangereg3,balangereg4,balangereg5,balancereg6, type = "html")

html_print(HTML(htmloutput))
```

## Baseline DID

### Risk Scores
```{r}
reg1 <- felm(avelsir ~ ccf + post + ccf*post year region avenumberarrivals2008_2010 avelsir2008_2010 avepctblack2008_2010 |loc + year + calandermonth|0|0, data=reg_data)
reg2 <- felm(avelsir ~ ccf + post + ccf*post |loc + year + calandermonth|0|0, data=reg_data)

htmloutput <- stargazer(reg1,reg2, type = "html")

html_print(HTML(htmloutput))
```

### Race
```{r}
reg1 <- felm(blackarrivals ~ ccf + post + ccf*post year region avenumberarrivals2008_2010 avelsir2008_2010 avepctblack2008_2010 |loc + year + calandermonth|0|0, data=reg_data)
reg2 <- felm(blackarrivals ~ ccf + post + ccf*post |loc + year + calandermonth|0|0, data=reg_data)

htmloutput <- stargazer(reg1,reg2, type = "html")

html_print(HTML(htmloutput))
```

### Offence Types
```{r}
# Violent
reg1 <- felm(arrivals_violent ~ ccf + post + ccf*post year region avenumberarrivals2008_2010 avelsir2008_2010 avepctblack2008_2010 |loc + year + calandermonth|0|0, data=reg_data)
reg2 <- felm(arrivals_violent ~ ccf + post + ccf*post |loc + year + calandermonth|0|0, data=reg_data)

# Drug
reg1 <- felm(arrivals_drug ~ ccf + post + ccf*post year region avenumberarrivals2008_2010 avelsir2008_2010 avepctblack2008_2010 |loc + year + calandermonth|0|0, data=reg_data)
reg2 <- felm(arrivals_drug ~ ccf + post + ccf*post |loc + year + calandermonth|0|0, data=reg_data)

# Property
reg1 <- felm(arrivals_property ~ ccf + post + ccf*post year region avenumberarrivals2008_2010 avelsir2008_2010 avepctblack2008_2010 |loc + year + calandermonth|0|0, data=reg_data)
reg2 <- felm(arrivals_property ~ ccf + post + ccf*post |loc + year + calandermonth|0|0, data=reg_data)
htmloutput <- stargazer(reg1,reg2, type = "html")

# Public Order
reg1 <- felm(arrivals_public ~ ccf + post + ccf*post year region avenumberarrivals2008_2010 avelsir2008_2010 avepctblack2008_2010 |loc + year + calandermonth|0|0, data=reg_data)
reg2 <- felm(arrivals_public ~ ccf + post + ccf*post |loc + year + calandermonth|0|0, data=reg_data)
htmloutput <- stargazer(reg1,reg2,reg3, reg4, reg5, reg6, reg7, reg8, type = "html")


html_print(HTML(htmloutput))
```


## Baseline Event Studies

```{r}

```

