---
title: "Halfway Houses and Pay-For-Performance Contracts"
#"Need to think of snappier title"
output: 
  revealjs::revealjs_presentation:
    theme: sky
    transition: slide
    css: style.css  # Include custom CSS
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

This slide deck is to organize findings, figures, and tables. There will be a seperate slide deck for presentations that will likely pull from figures and tables here

**Below are examples of various slide types**

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

# Introduction

# Background

## 
Figure documenting number of releases to CCCs, CCFs, and direct release. Time series if possible

##
Table comparing 3 year recidivism rates for halfway houses and direct release over sample period. Make the point that halfway houses often associated with worse outcomes. Cite popular press and Lee 2022

# Parallel trends
Figure showing time series of 3 year recidivism rate for 2008-2017 separately for CCCs and CCFs

- Highlight 2013, the year of the policy
- Cannot calculate 3 year recidivism rate after 2017 because data stops at 2017

# Summary Stats
Summary stats table for all residents released from halfway houses. 

- Split by CCC and CCF. 
- Race, offense by category (exactly how is TBD), age a release, LSI-R, years in PA DOC (will need to construct from movement file. Difference between year first shows up in movement file and year released from halfway house)
- **Will give insight into how CCC and CCF resident's are different**. Would be nice if they are not. If they are, lean on parallel trends assumption  

# Event study plots: Individual outcomes
Below plots for individual level regs

- Try leads/lags at quarterly level or 1/2 year level

## Recidivism

## Employment

## Time to recommitment
Restrict to indiviuals who are eventually recommitted to PA DOC.

# Event study plots: Facility level outcomes
Below are plots for facility level regs

- Try leads/lags at quarterly level or 1/2 year level

## Incoming LSI-R averages

## Incoming offense type


# DID table
Main findings. 

Repeat above outcomes in a single table or split into two tables if too crowded.

# Placebo tests
Rerun regs with treatment year before and after 2013.

# Heterogeneity

## Race

## Age

## Offence

# Mechanisms
Need to figure out what facilities did to change if anything. 

How to test? ?

# Cost Savings?
This slide is a placeholder to remember to discuss back-of-the envelope calculations on benefits of program

